Using structural and evolutionary information to correct RNA pyrosequencing errors in non-coding RNAs

### 2013-05-24 JCB/conclusion_JCB.tex

\TODOJerome{Etoffer la conclusion}
In this article we presented a new and efficient way of exploring the mutational landscape of an RNA under structural constraints,
and apply our techniques to identify and fix sequencing errors. In addition, we introduce a new
scoring scheme combining the nearest-neighbour energy model to new isostericity matrices in order to account for geometrical
discrepancies occurring during base pair replacements.
The algorithm runs in  $\Theta(n\cdot(|\Omega|+m^2))$ time and $\Theta(n\cdot(|\Omega|+m))$ memory, where $n$ is the length of the RNA,
$m$ the number of mutations and $\Omega$ the size of the multiple sequence alignment.

By combining  into \texttt{RNApyro} these two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 we created a tool predicting the positions
 yielding point-wise sequencing error and correcting them.
We validated our model with the 5s rRNA,
as presented in Sec.~\ref{sec:results}.
We observed that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
This indicates that an exploitable signal is captured by the isostericity.
Importantly, the implementation is fast enough for practical applications.

>>>>

\TODOJerome{Etoffer la conclusion}
In this article we presented a new and efficient way of exploring the mutational landscape of an RNA under structural constraints,
and apply our techniques to identify and fix sequencing errors. In addition, we introduced a new scoring scheme to measure the
likelihood of sequencing errors that combines the classical nearest-neighbour energy model parameters \cite{Turner2010} to the recently introduced
isostericity matrices \cite{Stombaugh2009}. The latter accounting for geometrical discrepancies occurring during base pair replacements.
Importantly, our algorithm runs in  $\Theta(n\cdot(|\Omega|+m^2))$ time and $\Theta(n\cdot(|\Omega|+m))$ memory, where $n$ is the length of the RNA,
$m$ the number of mutations and $\Omega$ the size of the multiple sequence alignment. This achievement enables us to envision applications to high-throughput sequencing pipe-lines.

By combining these two approaches into \texttt{RNApyro} ,  the 
mutational landscape exploration and the pseudo energy model,
 we created a tool predicting the positions
 yielding point-wise sequencing error and correcting them.
We validated our model with the 5s rRNA,
as presented in Sec.~\ref{sec:results}.
We observed that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
This indicates that an exploitable signal is captured by the isostericity.
Importantly, the implementation is fast enough for practical applications.
